### 2016-04-17 ALMA/Cycle4/RXJ.tex
ready for DR 2nd round

\documentclass[12pt,a4paper]{article}  %% DO NOT CHANGE to 11pt or less !
% \usepackage{apjfonts}
\usepackage{times}
\usepackage{graphics,graphicx}
\usepackage[update,prepend]{epstopdf}
\usepackage[innercaption]{sidecap}
\usepackage{subcaption}
\usepackage{amssymb, amsmath}	       
\usepackage{xspace}				
\usepackage{natbibspacing, natbib}
\usepackage{aas_macros}
\usepackage{wrapfig}
\usepackage{floatrow}

\newcommand{\ncrit}{\mbox{$n_{\rm crit}$}\xspace}
\newcommand{\comol}{$^{12}$CO\xspace}
\newcommand{\Lsun}{\mbox{L$_{\odot}$}\xspace}
\newcommand{\LIR}{\mbox{L$_{\rm IR}$}\xspace}
\newcommand{\LFIR}{\mbox{L$_{\rm FIR}$}\xspace}
\newcommand{\rarr}{$\rightarrow$}
\newcommand{\aco}{\mbox{CO($J$=1\rarr0)}\xspace}
\newcommand{\bco}{\mbox{CO($J$=2\rarr1)}\xspace}
\newcommand{\cco}{\mbox{CO($J$=3\rarr2)}\xspace}
\newcommand{\eco}{\mbox{CO($J$=5\rarr4)}\xspace}
\newcommand{\rot}[3][HCN]{\mbox{#1($J$=#2\rarr#3)}\xspace} 
% default HCN; usage \rot[HCN]{3}{2} or \rot[\hcop]{4}{3}
\newcommand{\ahcn}{HCN($J$=1\rarr0)\xspace}
\newcommand{\dhcn}{HCN($J$=4\rarr3)\xspace}
\newcommand{\hcop}{HCO$^+$\xspace}
\newcommand{\ahcop}{\mbox{HCO$^+$($J$=1\rarr0)}}
\newcommand{\dhcop}{HCO$^+$($J$=4\rarr3)\xspace}
\newcommand{\Lp}[1][CO]{\mbox{$L^{\prime}_\textrm{\fontsize{8pt}{12pt}\selectfont{#1}}$}}
\newcommand{\LpU}{\mbox{K\,\,km\,\,s$^{-1}$\,\,pc$^2$}}
\newcommand{\kms}{km\,s$^{-1}$\xspace}
\newcommand{\pmOne}{\mbox{$^{-1}$}\xspace}
\newcommand{\Fig}[1]{Fig.~\ref{fig:#1}}
\newcommand{\Eq}[1]{Equation~\ref{eq:#1}}

@@

\renewcommand\floatpagefraction{.9}
\renewcommand\topfraction{.9}
\renewcommand\bottomfraction{.9}
\renewcommand\textfraction{.1}
% between fig
\setlength{\textfloatsep}{10pt plus 1.0pt minus 2.0pt}
\setlength{\floatsep}{10pt plus 1.0pt minus 2.0pt}
\setlength{\intextsep}{10pt plus 1.0pt minus 2.0pt}
% between figure and caption
\setlength{\abovecaptionskip}{10pt plus 0pt minus 0pt}
\setlength{\parskip}{0.01em}
\usepackage[small,tiny,compact]{titlesec}

@@

While the ISM in local ULIRGs has been studied in great detail with ALMA,
forming a rich inventory of molecular transitions that serves as the template for 
understanding high-z galaxies and galaxy evolution \citep[e.g.][]{Rangwala15a}, a wide knowledge gap persists
between $z$=0 and the epoch when most stars are formed in the universe ($z\sim$2). 
Understanding galaxy populations at the epoch when the build-up of stellar mass across cosmic
time is steeply rising is thus critical and we here aim to bridge this gap by testifying
correlations and properties found locally out to high/moderate redshifts by observing the 
dynamical structure of the different molecular gas components
in the quadruply lensed galaxy RXJ1131-1231 and its dust-obscured 
companion at $z_{\rm CO}$$\sim$0.65.
%to bridge the gap between nearby ULIRGs and their high-z analogues.

@@

While \comol emission traces the total molecular distribution and dynamics,
high-dipole moment molecules such as HCN and \hcop are expected to trace the 
properties of the denser, actively star-forming gas. Indeed, a tight correlation between \ahcn and \LIR 
(proxy for SFR) has been found in nearby galaxies and local giant molecular 
clouds (GMC; \citealt[hereafter GS04]{Gao04a}; \citealt{Wu05}), 
suggesting HCN is a faithful tracer of the star-forming dense gas.
% and that the origin can be attributed to the fundamental units of star formation. 
This has been supported by the linear correlations in 
\LIR-\Lp[\dhcn] and \LIR-\Lp[\dhcop] found recently \citep[see \Fig{SF}]{Zhang14a}, which also highlight 
the great utility of these mid-$J$ lines observable for galaxies at $z$$>$0.06.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
% \section*{Science Target RXJ 1131-1231: a demonstrative case at high-z}
% \vspace{-0.25em}
\noindent {\bf Science Target RXJ 1131-1231: a demonstrative case at high-z}

%\begin{figure}[!tbhp]
%\centering
%\includegraphics[trim= 10 20 15 0, clip, scale=0.3]{Fig/F555W} % &
%\hspace{-0.5em}
%\includegraphics[trim= 10 0 0 0, clip, scale=0.37]{Fig/Manipulate_figsCROP}
%\vspace{-1em}
%\caption{ \fontsize{10pt}{12pt}\selectfont 
%{
%\textbf{Stellar light distribution in the AGN host galaxy of RXJ 1131-1231 and its reconstructed source plane
%morphology}
%{\em Left:} The rest-frame UV emission (tracing recent star formation) 
%is lensed into an almost complete Einstein ring with diameter $\sim$ 3.8". 
%{\em Right:} Lens modelling of the optical emission identifies complex structure in the host galaxy and
%an optically faint companion (white; \citealt{Claeskens06a}), 
%which we have recently confirmed by modeling \bco emission detected with NOEMA
%(\Fig{combine}; Leung \& Riechers, in prep.). 
%We here propose to study
%the ISM conditions in this AGN-starburst composite system and offers an unparalleled
%view into the early universe, with finer
%detail than otherwise possible with current facilities. 
%}
%\label{fig:HST}}
%\end{figure}

\begin{figure}[!tbhp]
\centering
\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,center},capbesidewidth=0.4\textwidth}}]{figure}[\FBwidth]
{
\hspace{-0.35em}
\vspace*{-0.55em}
\caption{ \fontsize{10pt}{12pt}\selectfont 
{
\textbf{Stellar light distribution in the AGN host galaxy of RXJ 1131-1231 and its reconstructed source plane
morphology}
{\em Left:} The rest-frame UV emission (tracing recent star formation) 
is lensed into an almost complete Einstein ring with diameter $\sim$ 3.8". 
{\em Right:} Lens modelling of the optical emission identifies complex structure in the host galaxy and
an optically faint companion (white; \citealt{Claeskens06a}), 
which we have recently confirmed by modeling \bco emission detected with NOEMA
(\Fig{combine}; Leung \& Riechers, in prep.). 
We here propose to study
the ISM conditions in this AGN-starburst composite system and offers an unparalleled
view into the early universe, with finer
detail than otherwise possible with current facilities. 
}
\label{fig:HST}}}
{\hspace{-1em}
\includegraphics[trim= 10 20 15 0, clip, scale=0.28]{Fig/F555W}
\hspace{-1.5em}
\includegraphics[trim= 10 0 0 0, clip, scale=0.32]{Fig/Manipulate_figsCROP}
\vspace{-1em}
}
\end{figure}

RXJ 1131-1231 is a quadruply imaged AGN with its host galaxy lensed 
into a partial Einstein ring (\Fig{HST}). 
HST observations (rest-frame UV) have revealed distinct emission 
from recent star formation (lensing arcs) and from the AGN (bright knots) in the background galaxy \citep{Sluse03a},
demonstrating the great potential for probing the 
ISM conditions in detail. Lens modeling carried out on optical images shows
that the AGN resides in a star-forming region of size $\sim$0.15" ($\sim$1 kpc)
in its host galaxy, which itself is 1" across ($\sim$7 kpc), and made it possible to identify
seven distinct structures in the source plane (\Fig{HST}). Remarkably, emission originating from 
a spatially offset region ($\sim$2.4 kpc away) from the AGN host galaxy has been identified and found 
to be $\sim$700 pc in size \citep{Brewer08a}, indicating a nearby companion galaxy. 
We have recently confirmed that both galaxies are at the same redshift by detecting their 
\rot[CO]{2}{1} emission and lens-modeling the distribution of the gas in velocity space (\Fig{combine}f), 
verifying that the both are gas-rich (Leung \& Riechers, in prep.). 
Our SED modeling of the dust continuum emission up to 500\,$\mu$m finds $L_{\rm IR}\sim6\times$10$^{12}$\Lsun 
(corrected for lensing). Hence, this target is a gas-rich ULIRG merger at $z$$\sim$0.7 caught in the act.

@@

The \eco observations at 0.15" are complementary to the optical images,
allowing a comparison between the stellar and gas distribution. 
%{\bf The proposed observations will provide the data tracing 
% the warm, excited, dense molecular gas distribution and kinematics, 
% which we will compare against the diffuse component (traced by our already obtained lower-J CO data). 
% OR 
Additionally, since \eco, \dhcn and \dhcop trace the warm, excited, dense molecular gas,
this will allow us to compare against the relatively unperturbed large-scale 
molecular environment and the dynamical mass with our existing lower-$J$ CO data.
% to study the
% gas distribution and kinematics.
Such comparison are key to understanding the processes and timescales regulating star-formation 
in ULIRG/merger, and examine how they differ from other galaxy populations.

@@

\underline{\bf Spectral line energy distributions (SLED) and SF Law:}
On top of using \dhcn and \hcop as AGN/SB diagnostic, another 
 aspect 
 %for obtaining the proposed line observations 
 is to 
% constrain the ISM conditions by fitting radiative transfer models.
% since these molecular species
% have different excitation criteria. %Therefore, 
%In combination 
combine them with \eco %, \dhcn, and \dhcop line emission
and our existing low-$J$ CO data to perform radiative transfer/large velocity gradient (LVG) modeling 
% [with assumptions on their relative abundances] 
to constrain the physical conditions 
(e.g. density and gas kinetic temperature) of the multi-phase molecular gas.
The \dhcn and \dhcop lines are essential as they trace beyond the $J$-transition of the CO SLED turnover
(typically beyond $J$=6\rarr5 in local (U)LIRGs and high-z starbursts; \citealt{Greve14a}).
% and since \eco traces the high kinetic temperature component. 
In addition, since ISM studies of high-z galaxies typically adopt local SLED for comparison \citep[e.g.][]{Bothwell13a}
and/or for asserting assumptions on the conditions of these high-z galaxies.
%[due to the sparsely sampled SLED at high-z \citep{CW13}].
Our observations will thus form a template at z$\sim$0.7 
for these high-z studies.

The ``star-formation law" (%$\Sigma_{\rm SFR}$=$A\Sigma^N_{gas}$ or 
log\LIR=$\alpha$ log\Lp[X]+$\beta$)
is one of the key ingredients % /observational constraints 
for theoretical models as it entails the physical processes 
of star-formation and its dependence on the ISM 
%(in the slopes and normalizations; 
(e.g. \citealt{Narayanan14a}).
% Observational constraints for the \LIR-\Lp[X] (\Lp of different lines) relations are vital.
However, the \LIR-\Lp[X] at high critical density are currently poorly constrained due to the lack of observations 
and are largely limited to the nearby universe
\citep[\Fig{SF}; ][]{Greve14a}. Our proposed observations will help delineate 
the slopes at high critical densities and 
explore the linear correlations found 
locally in \Lp[\dhcn]-\LIR and \Lp[\dhcop]-\LIR \citep[\Fig{SF}; ][]{Zhang14a} at higher redshifts.
%
\begin{figure*}[!tbph]
\centering
\includegraphics[trim=15 0 5 10, clip, width=0.23\textwidth]{Fig/Zhang}
\includegraphics[trim=5 5 5 10, clip, width=0.23\textwidth]{Fig/Zhang2}
\includegraphics[trim=10 0 0 5, clip, width=0.4\textwidth]{Fig/Greve14Fig2}
\caption{ \fontsize{10pt}{12pt}\selectfont {\textbf{Integrated form of the SF law: log \LFIR = $\alpha$ log \Lp[X]+$\beta$.}}
{\em Left \& middle:}
A linear correlation between \LIR-\dhcn and \LIR-\dhcop have been established toward nearby galaxies 
with \LIR$\sim$10$^9$-10$^{12}$\Lsun \citep{Zhang14a}, demonstrating the utility of mid-$J$ lines in tracing 
the star-forming dense gas, which will be routinely mapped in high-z galaxies with ALMA.
Our proposed observations will testify the linearity by adding measurements of a ULIRG at z$\sim$0.7, 
% extending the statistics/data to higher redshifts, 
and unveil potential deviations at higher redshift.
{\em Right:} \textbf{Constraints on the SF law 
with line transitions of different \ncrit.}
Most observations are incompatible with current model predictions (gray shaded area),
especially for \dhcn
\citep{Greve14a}.
Our proposed observations will thus reduce the uncertainties on the slopes at high critical densities
and improve our current understanding of galaxy evolution.
\label{fig:SF}}
\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent {\bf Technical overview}
We propose to observe the \eco line at $\sim$0.15" resolution
and the \dhcn and \dhcop lines at $\sim$0.7", assuming a line width 
(FWHM) of 700\kms based on our \bco data
(\Fig{combine}a) and a source size from our lens model (see details in TJ).
%, which takes into account the asymmetric line emission and spatial extent due to differential lensing. 
We thus expect the source to be resolved over 153 beams 
and 7 beams at 0.15" and 0.7", respectively. 
We compute the target sensitivities for both science goals using \bco line flux. 
For \eco, we adopt conservative 
line ratios measured for SMGs \citep[][see TJ for details]{CW13},
and those based on (U)LIRGs for \dhcn (GS04; \citealt{Papadopoulos07a}).
For \dhcop, we adopt the line ratio \dhcn/\dhcop found in ULIRGs 
\citep{Greve09a}. 
We use the most stringent sensitivity estimates 
among \dhcn and \dhcop as our sensitivity goal for science goal $1$. %The latter sets the overall requirement. 
To secure enough S/N for lens modeling, 
we require a minimum of 8$\sigma$ of 0.47 mJy beam\pmOne and 0.07 mJy beam\pmOne
per 150 \kms channel 
%to reconstruct the dynamical structure in the source plane 
for the science goals, respectively. 
We therefore request a \textbf{total time of 7.0 hours}.% to complete our science goals.

@@

\begin{figure*}[tbph]
\centering
\includegraphics[trim=25 6 5 5, clip, width=0.75\textwidth]{Fig/combine}
\caption{ \fontsize{10pt}{12pt}\selectfont {}
% CO2-1 line profile
{\em (a):} \textbf{PdBI \rot[CO]{2}{1} dynamically resolved line profile}
The \bco spectrum showing a double-horned, highly asymmetric line profile, which arises due to 
differential lensing across the kinematic components of the source (see (f)).
% HST
{\em (b):}  \textbf{Detection of a gas-rich merger with spatial variations traced by \bco}
The (red, green, blue) contours correspond to the velocity-integrated 
line flux of different velocity channels (red wing, line center, blue wing) in our \rot[CO]{2}{1} data. 
{\em (c):} \textbf{RXJ1131-1231 kinematics in \bco}
% 1st order
The observed velocity gradient is suggestive of a kinematically ordered disk at 
the current resolution limit.
{\em (d):} \textbf{RXJ1131-1231 dynamics in \bco}
% 2nd order
Velocity dispersion map of the \bco emitting gas. 
However, limited by the spatial resolution, beam smearing strongly decreases
large-scale velocity gradients and increases observed dispersion.
% RGB spectra
{\em (e): } \textbf{Differential lensing with spatial variations}
Overlay of spectra taken at regions along the strongest velocity gradient, demonstrating 
differential lensing of the different kinematic components of the galaxy. 
% Lens model
{\em (f): } \textbf{Dynamical lens model}
Velocity channels of the CO emission toward the gas-rich merger (red contours) overlaid on our best-fit 
lens model for each velocity bin (grayscale). 
The foreground lensing galaxy is represented by a black dot, and 
the beam size is shown in the bottom right corner.
Clearly, there are spatial variations across different kinematic components.
The reconstructed source morphology (magenta ellipses) is suggestive of a kinematically ordered galaxy. 
However, at the spatial resolution of our data, we cannot definitively infer its true morphology due to beam smearing. 
Given the presence of a companion galaxy within 2.4 kpc, high-resolution 
imaging is thus necessary to unambiguously determine the nature that gives rise to the observed velocity gradient
and dynamics, as proposed here.
This will confirm if the system is rotationally supported or highly turbulent 
(tidally disrupted) and allow us to investigate the major mechanisms responsible 
for the starburst in the AGN host galaxy
and investigate whether dominant mode of star formation is GMC-like in a rotating disk or due to fragmentation of
dynamically unstable gas-rich disk. 
We here aim to spatially and dynamically resolve the dense, excited gas emission, 
which will allow us to unambiguously examine the dynamic structure of the ISM in 
the distant merger and provide observational constraints on the star-formation and 
stellar-assembly history at the epoch where the SFR density is steeply 
rising across cosmic times.
\label{fig:combine}}
\end{figure*}
%

>>>>

\documentclass[12pt,a4paper]{article} 
\usepackage{times}
\usepackage{graphics,graphicx}
\usepackage[update,prepend]{epstopdf}
\usepackage[innercaption]{sidecap}
\usepackage{subcaption}
\usepackage{amssymb, amsmath}	       
\usepackage{xspace}				
\usepackage{natbibspacing, natbib}
\usepackage{aas_macros}
\usepackage{wrapfig}
\usepackage{floatrow}

\newcommand{\ncrit}{\mbox{$n_{\rm crit}$}\xspace}
\newcommand{\comol}{$^{12}$CO\xspace}
\newcommand{\Lsun}{\mbox{L$_{\odot}$}\xspace}
\newcommand{\LIR}{\mbox{$L_{\rm IR}$}\xspace}
\newcommand{\LFIR}{\mbox{$L_{\rm FIR}$}\xspace}
\newcommand{\rarr}{$\rightarrow$}
\newcommand{\aco}{\mbox{CO($J$=1\rarr0)}\xspace}
\newcommand{\bco}{\mbox{CO($J$=2\rarr1)}\xspace}
\newcommand{\cco}{\mbox{CO($J$=3\rarr2)}\xspace}
\newcommand{\eco}{\mbox{CO($J$=5\rarr4)}\xspace}
\newcommand{\rot}[3][HCN]{\mbox{#1($J$=#2\rarr#3)}\xspace} 
% default HCN; usage \rot[HCN]{3}{2} or \rot[\hcop]{4}{3}
\newcommand{\ahcn}{HCN($J$=1\rarr0)\xspace}
\newcommand{\dhcn}{HCN($J$=4\rarr3)\xspace}
\newcommand{\hcop}{HCO$^+$\xspace}
\newcommand{\ahcop}{\mbox{HCO$^+$($J$=1\rarr0)}}
\newcommand{\dhcop}{HCO$^+$($J$=4\rarr3)\xspace}
\newcommand{\Lp}[1][CO]{\mbox{$L^{\prime}_\textrm{\fontsize{8pt}{12pt}\selectfont{#1}}$}}
\newcommand{\LpU}{\mbox{K\,\,km\,\,s$^{-1}$\,\,pc$^2$}}
\newcommand{\kms}{km\,s$^{-1}$\xspace}
\newcommand{\pmOne}{\mbox{$^{-1}$}\xspace}
\newcommand{\Fig}[1]{Fig.~\ref{fig:#1}}
\newcommand{\Eq}[1]{Equation~\ref{eq:#1}}

@@

\renewcommand\floatpagefraction{.9}
\renewcommand\topfraction{.9}
\renewcommand\bottomfraction{.9}
\renewcommand\textfraction{.1}
% between fig
\setlength{\textfloatsep}{10pt plus 1.0pt minus2.0pt}
\setlength{\floatsep}{10pt plus 1.0pt minus 2.0pt}
\setlength{\intextsep}{10pt plus 1.0pt minus 2.0pt}
\setlength{\parskip}{0.01em}
\usepackage[small,tiny,compact]{titlesec}

@@

While the ISM in local ULIRGs has been studied in great detail with ALMA,
forming a rich inventory of molecular transitions that serves as the template for 
understanding high-z galaxies and galaxy evolution \citep[e.g.][]{Rangwala15a}, a wide knowledge gap persists
between $z$=0 and the epoch when most stars are formed in the universe ($z$$\sim$2). 
Understanding galaxy populations at the epoch when the build-up of stellar mass across cosmic
time is steeply rising is thus critical and we here aim to bridge this gap by testifying
correlations and properties found locally out to high/moderate redshifts by observing the 
dynamical structure of the different molecular gas components
in the quadruply lensed galaxy RXJ1131-1231 and its dust-obscured 
companion at $z_{\rm CO}$$\sim$0.65.
%to bridge the gap between nearby ULIRGs and their high-z analogues.

@@

While \comol emission traces the total molecular distribution and dynamics,
high-dipole moment molecules such as HCN and \hcop are expected to trace the 
properties of the denser, actively star-forming gas. Indeed, a tight correlation between \ahcn and \LIR 
(proxy for SFR) has been found in nearby galaxies and local giant molecular 
clouds (GMC; \citealt[hereafter GS04]{Gao04a}; \citealt{Wu05}), 
suggesting HCN is a faithful tracer of the star-forming dense gas.
% and that the origin can be attributed to the fundamental units of star formation. 
This has been supported by the linear correlations in 
\LIR-\Lp[\dhcn] and \LIR-\Lp[\dhcop] found recently \citep[hereafter Z14; see \Fig{SF}]{Zhang14a}, which also highlight 
the great utility of these mid-$J$ lines observable for galaxies at $z$$>$0.06.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
% \section*{Science Target RXJ 1131-1231: a demonstrative case at high-z}
% \vspace{-0.25em}
\noindent {\bf Science Target RXJ 1131-1231: a demonstrative case at high-z}
\vspace{-0.7em}
%\begin{figure}[!tbhp]
%\centering
%\includegraphics[trim= 10 20 15 0, clip, scale=0.3]{Fig/F555W} % &
%\hspace{-0.5em}
%\includegraphics[trim= 10 0 0 0, clip, scale=0.37]{Fig/Manipulate_figsCROP}
%\vspace{-1em}
%\caption{ \fontsize{10pt}{12pt}\selectfont 
%{
%\textbf{Stellar light distribution in the AGN host galaxy of RXJ 1131-1231 and its reconstructed source plane
%morphology}
%{\em Left:} The rest-frame UV emission (tracing recent star formation) 
%is lensed into an almost complete Einstein ring with diameter $\sim$ 3.8". 
%{\em Right:} Lens modeling of the optical emission identifies complex structure in the host galaxy and
%an optically faint companion (white; \citealt{Claeskens06a}), 
%which we have recently confirmed by modeling \bco emission detected with NOEMA
%(\Fig{combine}; Leung \& Riechers, in prep.). 
%We here propose to study
%the ISM conditions in this AGN-starburst composite system and offers an unparalleled
%view into the early universe, with finer
%detail than otherwise possible with current facilities. 
%}
%\label{fig:HST}}
%\end{figure}

\begin{figure}[!tbhp]
\centering
\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,center},capbesidewidth=0.425\textwidth}}]{figure}[\FBwidth]
{
\hspace{-0.35em}
\vspace*{-0.55em}
\raggedleft
\caption{ \fontsize{10pt}{12pt}\selectfont 
{
\textbf{Stellar light distribution in the AGN host galaxy of RXJ 1131-1231 and its reconstructed source plane
morphology}
{\em Left:} The rest-frame UV emission (tracing recent star formation) 
is lensed into an almost complete Einstein ring with diameter $\sim$ 3.8". 
{\em Right:} Lens modeling of the optical emission identifies complex structures in the host galaxy and
an optically faint companion (white; \citealt{Claeskens06a}), 
which we have recently confirmed by modeling \bco emission detected with NOEMA
(\Fig{combine}; Leung \& Riechers, in prep.). 
We here propose to study
the ISM conditions in this AGN-starburst composite system and offers an unparalleled
view into the early universe, with finer
detail than otherwise possible with current facilities. 
}
\label{fig:HST}}}
{\hspace{-1em}
\includegraphics[trim= 10 20 15 0, clip, scale=0.28]{Fig/F555W}
\hspace{-1.5em}
\includegraphics[trim= 10 0 0 0, clip, scale=0.3]{Fig/Manipulate_figsCROP}
\vspace{-1em}
}
\end{figure}
\vspace{-0.8em}
RXJ 1131-1231 is a quadruply imaged AGN with its host galaxy lensed 
into a partial Einstein ring (\Fig{HST}). 
HST observations (rest-frame UV) have revealed distinct emission 
from recent star formation (lensing arcs) and from the AGN (bright knots) in the background galaxy \citep{Sluse03a},
demonstrating the great potential for probing the 
ISM conditions in detail. Lens modeling carried out on optical images shows
that the AGN resides in a star-forming region of size $\sim$0.15" ($\sim$1 kpc)
in its host galaxy, which itself is 1" across ($\sim$7 kpc), and made it possible to identify
seven distinct structures in the source plane (\Fig{HST}). Remarkably, emission originating from 
a spatially offset region ($\sim$2.4 kpc away) from the AGN host galaxy has been identified and found 
to be $\sim$700 pc in size \citep{Brewer08a}, indicating a nearby companion galaxy. 
We have recently confirmed that both galaxies are at the same redshift by detecting their 
\rot[CO]{2}{1} emission and lens-modeling the distribution of the gas in velocity space (\Fig{combine}f), 
verifying that the both are gas-rich (Leung \& Riechers, in prep.). 
Our SED modeling of the dust continuum emission up to 500\,$\mu$m finds $L_{\rm IR}\sim6\times$10$^{12}$\Lsun 
(corrected for lensing). Hence, this target is a gas-rich ULIRG merger at $z$$\sim$0.7 caught in the act.

@@

The \eco observations at 0.15" are complementary to the optical images,
allowing a comparison between the stellar and gas distribution. 
%{\bf The proposed observations will provide the data tracing 
% the warm, excited, dense molecular gas distribution and kinematics, 
% which we will compare against the diffuse component (traced by our already obtained lower-J CO data). 
% OR 
Additionally, since \eco, \dhcn and \dhcop trace the warm, excited, dense molecular gas,
this will allow us to compare against the relatively unperturbed large-scale 
molecular environment and the dynamical mass with our existing lower-$J$ CO data.
% to study the
% gas distribution and kinematics.
Such comparison are key to understand the processes and timescales regulating star-formation 
in ULIRG/merger, and examine how they differ from other galaxy populations.

@@

\underline{\bf Spectral line energy distributions (SLED) and the SF Law:}
On top of using \dhcn and \hcop as AGN/SB diagnostic, another 
 aspect 
 %for obtaining the proposed line observations 
 is to 
% constrain the ISM conditions by fitting radiative transfer models.
% since these molecular species
% have different excitation criteria. %Therefore, 
%In combination 
combine them with \eco %, \dhcn, and \dhcop line emission
and our existing low-$J$ CO data to perform radiative transfer modeling 
% [with assumptions on their relative abundances] 
to constrain the physical conditions 
(e.g. density and gas kinetic temperature) of the multi-phase molecular gas.
The \dhcn and \dhcop lines are essential as they trace beyond the $J$-transition of the CO SLED turnover
(typically beyond $J$=6\rarr5 in local (U)LIRGs and high-z starbursts; \citealt{Greve14a}).
% and since \eco traces the high kinetic temperature component. 
In addition, since ISM studies of high-z galaxies typically adopt local SLED for comparison \citep[e.g.][]{Bothwell13a}
and/or for asserting assumptions on the conditions of these high-z galaxies.
%[due to the sparsely sampled SLED at high-z \citep{CW13}].
Our observations will thus form a template at z$\sim$0.7 
for these high-z studies.

The ``star-formation law" (%$\Sigma_{\rm SFR}$=$A\Sigma^N_{gas}$ or 
log\LIR=$\alpha$ log\Lp[X]+$\beta$)
is one of the key ingredients % /observational constraints 
for theoretical models as it encodes the physical processes 
of star-formation and its dependence on the ISM 
%(in the slopes and normalizations; 
(e.g. \citealt{Narayanan14a}).
% Observational constraints for the \LIR-\Lp[X] (\Lp of different lines) relations are vital.
However, the \LIR-\Lp[X] at high critical density are currently poorly constrained due to the lack of observations 
and are largely limited to the nearby universe
\citep[\Fig{SF};][]{Greve14a}. Our proposed observations will help delineate 
the slopes at high critical densities and 
explore the linear correlations found 
locally in \Lp[\dhcn]-\LIR and \Lp[\dhcop]-\LIR (\Fig{SF}; Z14) at higher redshifts.
%
\begin{figure*}[!tbph]
\centering
\includegraphics[trim=15 0 5 10, clip, width=0.2\textwidth]{Fig/Zhang}
\includegraphics[trim=5 5 5 10, clip, width=0.2\textwidth]{Fig/Zhang2}
\includegraphics[trim=10 0 0 5, clip, width=0.38\textwidth]{Fig/Greve14Fig2}
\caption{ \fontsize{10pt}{12pt}\selectfont {\textbf{The SF law: log \LIR = $\alpha$ log \Lp[X]+$\beta$.}}
{\em Left \& middle:}
A linear correlation between \LIR-\dhcn and \LIR-\dhcop have been established toward nearby galaxies 
% with \LIR$\sim$10$^9$-10$^{12}$\Lsun 
(Z14), demonstrating the utility of mid-$J$ lines in tracing 
the star-forming dense gas, which will be routinely mapped in high-z galaxies with ALMA.
Our proposed observations will testify the linearity by adding measurements of a ULIRG at z$\sim$0.7, 
% extending the statistics/data to higher redshifts, 
and unveil potential deviations at higher redshift.
{\em Right:} \textbf{Constraints on the SF law 
with line transitions of different \ncrit.}
Most observations are incompatible with current model predictions (gray shaded area),
especially for \dhcn
\citep{Greve14a}.
Our proposed observations will thus reduce the uncertainties on the slopes at high critical densities
and improve our current understanding of galaxy evolution.
\label{fig:SF}}
\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent {\bf Technical overview}
We propose to observe the \eco line at 0.15" resolution
and the \dhcn and \dhcop lines at 0.7", assuming a line 
of 700\kms based on our \bco data
and a source size from our lens model (see details in TJ).
%, which takes into account the asymmetric line emission and spatial extent due to differential lensing. 
We thus expect the source to be resolved over 153 beams 
and 7 beams at 0.15" and 0.7", respectively. 
We compute the target sensitivities for both science goals based on the \bco line flux. 
For \eco, we adopt conservative 
line ratios measured for SMGs \citep[][see TJ for details]{CW13},
and those based on (U)LIRGs for \dhcn (GS04; \citealt{Papadopoulos07a}).
For \dhcop, we adopt the line ratio \dhcn/\dhcop found in ULIRGs 
\citep{Greve09a}. 
We use the most stringent sensitivity estimates 
among \dhcn and \dhcop as our sensitivity goal for science goal $1$. %The latter sets the overall requirement. 
To secure enough S/N for lens modeling, 
we require a minimum of 8$\sigma$ of 0.47 mJy beam\pmOne and 0.07 mJy beam\pmOne
per 150 \kms channel 
%to reconstruct the dynamical structure in the source plane 
for the science goals, respectively. 
We therefore request a \textbf{total time of 7.0 hours}.% to complete our science goals.

@@

\begin{figure*}[tbph]
\centering
\includegraphics[trim=7 6 5 5, clip, width=0.75\textwidth]{Fig/combine}
\caption{ \fontsize{10pt}{12pt}\selectfont {}
{\em (a):}
The \bco spectrum of RXJ1131-1231 shows a double-horned, highly 
asymmetric line profile, which arises due to differential lensing.
{\em (b):}
Spatial variations traced by \bco as shown by the (red, green, blue) contours corresponding
to the line flux of different velocity channels (red wing, line center, blue wing). 
{\em (c):} 
The observed velocity gradient is suggestive of a kinematically ordered disk at 
the current resolution limit.
{\em (d):} 
Velocity dispersion map of the \bco emitting gas. 
However, limited by the spatial resolution, beam smearing strongly decreases
large-scale velocity gradients and increases observed dispersion.
% RGB spectra
{\em (e): }
Overlay of spectra taken at three locations along the strongest velocity gradient, demonstrating 
differential lensing of the different kinematic components of the galaxy. 
% Lens model
{\em (f): }
Velocity channels of the CO emission toward the gas-rich merger (red contours) overlaid on our best-fit 
lens model for each velocity bin (grayscale). 
The foreground lensing galaxy is represented by a black dot, and 
the beam size is shown in the bottom right corner.
Clearly, there are spatial variations across different kinematic components.
The reconstructed source morphology (magenta ellipses) is suggestive of a kinematically ordered galaxy. 
Given the presence of a companion galaxy within 2.4 kpc and beam smearing effects, high-resolution 
imaging is thus necessary to unambiguously determine the nature that gives rise to the observed velocity gradient
and dynamics, as proposed here.
This will confirm if the system is rotationally supported or highly turbulent 
(tidally disrupted) and allow us to investigate the major mechanisms responsible 
for the starburst in the AGN host galaxy
and investigate whether dominant mode of star formation is GMC-like in a rotating disk or due to fragmentation of
dynamically unstable gas-rich disk. 
{\bf We here aim BLAH}
and provide observational constraints on the star-formation and 
stellar-assembly history at the epoch where the SFR density is steeply 
rising across cosmic times.
\label{fig:combine}}
\end{figure*}
%
